---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gghisse

<!-- badges: start -->
<!-- badges: end -->

The goal of `gghisse` is to provide additional ways to visualize results from `hisse` family models ([HiSSE](https://cran.r-project.org/web/packages/hisse/index.html) objects)

## Installation

<!-- You can install the released version of `gghisse` from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("gghisse") -->
<!-- ``` -->

The development version can be installed from from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("discindo/gghisse")
```

A CRAN submission is forthcoming.

## Web application

To see the main functionality and example code, visit the Shiny web application: https://diatom.shinyapps.io/hisse-web/

## Example usage

```{r}
library("gghisse")
data("diatoms")
processed_hisse <- gghisse::h_process_recon(hisse_recon=diatoms$cid4_recon)
hisse_rates_plot <- gghisse::h_scatterplot(
  processed_recon=processed_hisse,
  parameter="turnover")
```


As `gghisse` is built on top of `ggplot2`, modifications to `gghisse` plots are easy with the familiar `ggplot` functions. For example, changing X axis tick labels:

```{r}
hisse_rates_plot +
  scale_x_discrete(breaks=c(0,1), labels=c("plankton", "benthos"))
```

Or changing the  position of the legend

```{r}
hisse_rates_plot +
  scale_x_discrete(breaks=c(0,1), labels=c("plankton", "benthos")) +
  theme(legend.position="top")
```

Or using expressions (for Greek letters) in the axis labels

```{r}
hisse_rates_plot +
  scale_x_discrete(breaks=c(0,1), labels=c("plankton", "benthos")) +
  theme(legend.position="top") +
  labs(y=expression(paste(tau, "=", lambda, "+", mu))) +
  theme(axis.text.y=element_text(size=15))
```
